The \vspec{} Collection: A suite of utilities to model spectroscopic phase curves of 3D exoplanet atmospheres in the presence of stellar variability.

### 2024-08-15 src/tex/ms.tex
change to elsarticle format

% Define document class
\documentclass[twocolumn,linenumbers]{aastex631}
\usepackage{showyourwork}
\usepackage[version=4]{mhchem}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{natbib}

@@

\shorttitle{\vspec{}}
\shortauthors{Johnson et al.}

@@

% Title
% \title{The \vspec{} code: Spectroscopic phase curves of 3D exoplanet models in the presence of stellar variability}
\title{The \vspec{} Collection: A suite of utilities to model spectroscopic phase curves of 3D exoplanet atmospheres in the presence of stellar variability.}

\correspondingauthor{Ted M Johnson}
\email{ted.johnson@unlv.edu}

% \author{Ted M Johnson}
\author[0000-0002-1570-2203]{Ted M Johnson}
\affiliation{Southeastern Universities Research Association, 1201 New York Avenue NW, Suite 430, Washington, DC 20055, USA}
\affiliation{Center for Research and Exploration in Space Science and Technology, NASA Goddard Space Flight Center, 8800 Greenbelt Road, Greenbelt, MD 20771, USA}
\affiliation{NASA Goddard Space Flight Center \\
8800 Greenbelt Rd \\
Greenbelt, MD 20771, USA}
\affiliation{Nevada Center for Astrophysics, University of Nevada, Las Vegas, 4505 South Maryland Parkway, Las Vegas, NV 89154, USA}
\affiliation{Department of Physics and Astronomy, University of Nevada, Las Vegas, 4505 South Maryland Parkway, Las Vegas, NV 89154, USA}

\author{Cameron Kelahan}
\affiliation{Southeastern Universities Research Association, 1201 New York Avenue NW, Suite 430, Washington, DC 20055, USA}
\affiliation{Center for Research and Exploration in Space Science and Technology, NASA Goddard Space Flight Center, 8800 Greenbelt Road, Greenbelt, MD 20771, USA}
\affiliation{NASA Goddard Space Flight Center \\
8800 Greenbelt Rd \\
Greenbelt, MD 20771, USA}

\author{Avi M. Mandell}
\affiliation{NASA Goddard Space Flight Center \\
8800 Greenbelt Rd \\
Greenbelt, MD 20771, USA}

\author{Ashraf Dhahbi}
\affiliation{NASA Goddard Space Flight Center \\
8800 Greenbelt Rd \\
Greenbelt, MD 20771, USA}

\author{Tobi Hammond}
\affiliation{NASA Goddard Space Flight Center \\
8800 Greenbelt Rd \\
Greenbelt, MD 20771, USA}

\author{Thomas Barclay}
\affiliation{NASA Goddard Space Flight Center \\
8800 Greenbelt Rd \\
Greenbelt, MD 20771, USA}

\author{Veselin B. Kostov}
\affiliation{NASA Goddard Space Flight Center \\
8800 Greenbelt Rd \\
Greenbelt, MD 20771, USA}

\author{Geronimo L. Villanueva}
\affiliation{NASA Goddard Space Flight Center \\
8800 Greenbelt Rd \\
Greenbelt, MD 20771, USA}

% Abstract with filler text
\begin{abstract}
    We present the Variable Star PhasE Curve (\texttt{VSPEC}) Collection, a set of Python packages for simulating combined-light spectroscopic observations of 3-dimensional exoplanet atmospheres in the presence of stellar variability and inhomogeneity. \texttt{VSPEC} uses the Planetary Spectrum Generator's Global Emission Spectra (PSG/GlobES) application along with a custom-built multi-component time-variable stellar model based on a user-defined grid of stellar photosphere models to produce spectroscopic light curves of the planet-host system. \texttt{VSPEC} can be a useful tool for modeling observations of exoplanets in transiting geometries (primary transit, secondary eclipse) as well as orbital phase curve measurements, and is built in a modular and flexible configuration for easy adaptability to new stellar and planetary model inputs. We additionally present a set of codes developed alongside the core \texttt{VSPEC} modules, including the stellar surface model generator \texttt{vspec-vsm}, the stellar spectral grid interpolation code GridPolator, and a Python interface for PSG, \texttt{libpypsg}.
\end{abstract}

\keywords{Exoplanet, M dwarf}

% Main body with filler text
\section{Introduction}
\label{sec:intro}

@@

\begin{figure}
    \centering
    \gridline{\includegraphics[width=0.5\textwidth]{figures/facula_diagram.pdf}}
    \gridline{\includegraphics[width=0.5\textwidth]{figures/facula_depth.pdf}}
    \script{facula_depth.py}
    \caption{
        ``Hot Wall'' model of faculae. Faculae structure causes their contrast to be dependent on their distance from the center of the disk. {\bf Top}: Depiction of a facula on the limb of a star. The hot wall is exposed to the observer causing the pore to appear bright. At disk center, the cool floor is most visible. {\bf Bottom}: The effects of depression depth and viewing angle on facula brightness. The 3D structure of faculae is most apparent when radius $\sim$ depth. A toy flux model was used to demonstrate the shape of these curves, but in practice their magnitudes depend on stellar spectral models.
        }
    \label{fig:fac_struct}
\end{figure}

@@

\bibliography{syw,VSPEC}

>>>>

% Define document class
\documentclass[linenumbers,preprint,authoryear]{elsarticle}
\usepackage{showyourwork}
\usepackage[version=4]{mhchem}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{natbib}

@@

% \shorttitle{\vspec{}}
% \shortauthors{Johnson et al.}

@@

% Title
\title{The \vspec{} Collection: A suite of utilities to model spectroscopic phase curves of 3D exoplanet atmospheres in the presence of stellar variability.}

\author[1,2,3,4,5]{Ted M Johnson\corref{cor1}}
\ead{ted.johnson@unlv.edu}

\author[1,2,3]{Cameron Kelahan}

\author[3]{Avi M. Mandell}

\author[3]{Ashraf Dhahbi}

\author[3]{Tobi Hammond}

\author[3]{Thomas Barclay}

\author[3]{Veselin B. Kostov}
\author[3]{Geronimo L. Villanueva}

\cortext[cor1]{Corresponding Author}

\affiliation[1]{
    organization={Southeastern Universities Research Association},
    addressline={1201 New York Avenue NW, Suite 430},
    city={Washington, DC},
    postcode={20055},
    country={USA}
}
\affiliation[2]{
    organization={Center for Research and Exploration in Space Science and Technology, NASA Goddard Space Flight Center},
    addressline={8800 Greenbelt Road},
    city={Greenbelt, MD},
    postcode={20771},
    country={USA}
}
\affiliation[3]{
    organization={NASA Goddard Space Flight Center},
    addressline={8800 Greenbelt Road},
    city={Greenbelt, MD},
    postcode={20771},
    country={USA}
}
\affiliation[4]{
    organization={Nevada Center for Astrophysics, University of Nevada, Las Vegas},
    addressline={4505 South Maryland Parkway},
    city={Las Vegas, NV},
    postcode={89154},
    country={USA}
}
\affiliation[5]{
    organization={Department of Physics and Astronomy, University of Nevada, Las Vegas},
    addressline={4505 South Maryland Parkway},
    city={Las Vegas, NV},
    postcode={89154},
    country={USA}
} 
\affiliation[6]{
    organization={University of Maryland, Baltimore County},
    addressline={1000 Hilltop Cir},
    city={Baltimore, MD},
    postcode={21250},
    country={USA}
}

\begin{abstract}
    We present the Variable Star PhasE Curve (\texttt{VSPEC}) Collection, a set of Python packages for simulating combined-light spectroscopic observations of 3-dimensional exoplanet atmospheres in the presence of stellar variability and inhomogeneity. \texttt{VSPEC} uses the Planetary Spectrum Generator's Global Emission Spectra (PSG/GlobES) application along with a custom-built multi-component time-variable stellar model based on a user-defined grid of stellar photosphere models to produce spectroscopic light curves of the planet-host system. \texttt{VSPEC} can be a useful tool for modeling observations of exoplanets in transiting geometries (primary transit, secondary eclipse) as well as orbital phase curve measurements, and is built in a modular and flexible configuration for easy adaptability to new stellar and planetary model inputs. We additionally present a set of codes developed alongside the core \texttt{VSPEC} modules, including the stellar surface model generator \texttt{vspec-vsm}, the stellar spectral grid interpolation code GridPolator, and a Python interface for PSG, \texttt{libpypsg}.
\end{abstract}

\begin{keyword}
    Exoplanet Atmospheres, Stellar Variability, Spectroscopic Phase Curve, Open Source, Planetary Spectrum Generator
\end{keyword}

% Highlights:
% Instruments that characterize exoplanet atmospheres are sensitive to the effects of stellar inhomogeneities.
% We present VSPEC, a code to simulate observations of 3D planets in the presence of stellar variability and inhomogeneity.
% VSPEC, and the codes that support it, are open source, well documented, and available to the public.

\maketitle

\section{Introduction}
\label{sec:intro}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/facula_diagram.pdf}
    \includegraphics[width=0.5\textwidth]{figures/facula_depth.pdf}
    \script{facula_depth.py}
    \caption{
        ``Hot Wall'' model of faculae. Faculae structure causes their contrast to be dependent on their distance from the center of the disk. {\bf Top}: Depiction of a facula on the limb of a star. The hot wall is exposed to the observer causing the pore to appear bright. At disk center, the cool floor is most visible. {\bf Bottom}: The effects of depression depth and viewing angle on facula brightness. The 3D structure of faculae is most apparent when radius $\sim$ depth. A toy flux model was used to demonstrate the shape of these curves, but in practice their magnitudes depend on stellar spectral models.
        }
    \label{fig:fac_struct}
\end{figure}

@@

\bibliographystyle{elsarticle-harv}
\bibliography{syw,VSPEC}
